\section*{REFERENCS}
\scriptsize
\begin{enumerate}[leftmargin=0.75cm,label={[\arabic*]}]
% SECTION 1

\item R. Abbas and K. Michael, ``COVID-19 Contact Trace App Deployments: Learnings From Australia and Singapore,'' \textit{IEEE Consumer Electronics Magazine}, vol. 9, no. 5,  pp. 65-70. Jun. 2020. \url{10.1109/MCE.2020.3002490}

\item K. Kemp, ``Concealed data practices and competition law: why privacy matters,'' \textit{European Competition Journal}, vol. 16, no. 2-3, pp. 628-672. Nov. 2020. \url{doi.org/10.1080/17441056.2020.1839228}

% SECTION 2 
  \item M. McLeay, A. Radia and R. Thomas, ``Money creation in the modern economy,'' Bank of England, United Kingdom, (2014 Q1), [Online]. Available: \url{https://web.archive.org/web/20230406043405/https://www.bankofengland.co.uk/-/media/boe/files/quarterly-bulletin/2014/money-creation-in-the-modern-economy.pdf}

  \item Bank of International Settlements, ``The role of central bank money in payment systems,'' Committee on Payment and Settlement Systems, [Online]. Available: \url{https://web.archive.org/web/20230413061727/https://www.bis.org/cpmi/publ/d55.pdf}
  
  \item Federal Reserve Bank of Chicago, ``Modern Money Mechanics: A Workbook on Bank Reserves and Deposit Expansion'', United States of America, [Online]. Available: \url{https://web.archive.org/web/20230328005417/https://upload.wikimedia.org/wikipedia/commons/4/4a/Modern\_Money\_Mechanics.pdf}
  
  \item Reserve Bank of Australia, ``Government Bond Purchases.'' Market Operations. \url{https://web.archive.org/web/20230323033859/https://www.rba.gov.au/mkt-operations/government-bond-purchases.html}
  
  \item Reserve Bank of Australia, ``About RITS.'' Payments \& Infrastructure. \url{https://web.archive.org/web/20230318133024/https://www.rba.gov.au/payments-and-infrastructure/rits/about.html}
  
  \item E. S. Prasad, ``The Case for Central Bank Digital Currencies,'' in The Future of Money: How the Digital Revolution Is Transforming Currencies and Finance. Harvard University Press, 2021, pp. 152–185.

  \item   J. Huber, ``CBDC System Design Principles,'' in The Monetary Turning Point: From Bank Money to Central Bank Digital Currency (CBDC). Palgrave Macmillan, 2023, pp. 117–150.


  \item Bank of International Settlements, ``Central bank digital currencies,'' Committee on Payments and Market Infrastructures, [Online]. Available: \url{https://web.archive.org/web/20230413140543/https://www.bis.org/cpmi/publ/d174.pdf}

  \item OMFIF and IBM, ``Retail CBDCs: The next payments frontier,'' Official Monetary and Financial Institutions Forum, London, United Kingdom, [Online]. Available: \url{https://web.archive.org/web/20220901054304/https://www.omfif.org/wp-content/uploads/2019/11/Retail-CBDCs-The-next-payments-frontier.pdf}

  
  \item The Australian Senate, `Select Committee on Australia as a Technology and Financial Centre: Final Report', Australia, 2021, [Online]. Available: \url{https://web.archive.org/web/20230416044100/https://parlinfo.aph.gov.au/parlInfo/download/committees/reportsen/024747/toc\_pdf/Finalreport.pdf;fileType=application/pdf}

  \item Australian government, `Anti-Money Laundering and Counter-Terrorism Financing Act', 2006.

% SECTION 3

  \item N. Pocher and A. Veneris, ``Privacy and transparency in cbdcs: A regulation-by-design aml/cft scheme,'' in IEEE International Conference on Blockchain and Cryptocurrency (ICBC 2021), 2021.

  % Anonymisation

  \item D. Chaum, ``Blind Signatures for Untraceable Payments,'' in Advances in Cryptology. Springer, Boston, MA, 1983. \url{doi.org/10.1007/978-1-4757-0602-4_18}

  % SMPC

  \item S. Atapoor, N. P. Smart and Y. T. Alaoui, ``Private Liquidity Matching using MPC,'' in Cryptology ePrint Archive, Paper 2021/475, 2021.

  \item A C. Yao, ``How to Generate and Exchange Secrets,'' Proceedings of the 27th Annual IEEE Symposium on Foundations of Computer Science, pp. 162-167, 1986.

  % ZKP
  \item T. Sander and A. Ta–Shma, ``Auditable, Anonymous Electronic Cash,'' in Advances in Cryptology (CRYPTO '99), pp. 565-572, 1999. 

  \item J. Thaler, ``Zero-Knowledge Proofs and Arguments,'' in Proofs, Arguments, and Zero-Knowledge. Foundations and Trends in Privacy and Security, vol. 4, no. 2–4, pp. 117-660. \url{dx.doi.org/10.1561/3300000030}

  \item O. Goldreich, ``Zero Knowledge Proof Systems,'' in Foundations of Cryptography, pp. 143-254, Cambridge University Press, United Kingdom, December 2009.

  % RS  
  \item R. L. Rivest, A. Shamir and Y. Tauman, ``How to leak a secret,'' in Proceedings of the 7th International Conference on the Theory and Application of Cryptology and Information Security, Gold Coast, Australia, vol. 2248, pp. 552–565. Springer, Berlin, Heidelberg, December 2001.

  % HE
  \item R. L. Rivest, L. Aldeman and M. L. Dertouzos, ``On Data Banks and Privacy Homomorphisms,'' \textit{Foundations of Secure Computing}, vol. 4, pp. 169-179, Oct. 1978.

  \item X. Yi, R. Paulet and E. Bertino, ``Homomorphic Encryption,'' in Homomorphic Encryption and Applications. Springer. 2014. \url{doi.org/10.1007/978-3-319-12229-8_2}

% SECTION 4

  \item A. Fight, ``Introduction to Syndicated Loans,'' in Syndicated Lending, Elsevier Science, Sep. 2004. 

  \item Reserve Bank of Australia, ``Syndicated Lending,'' Australia, Sep. 2005. [Online]. Available: \url{https://web.archive.org/web/20230420083050/https://www.rba.gov.au/publications/bulletin/2005/sep/pdf/bu-0905-1.pdf}
  
  \item Reserve Bank of Australia, ``Project Atom: Exploring a Wholesale CBDC for Syndicated Lending,'' 2021, [Online]. Available: \url{https://web.archive.org/web/20230319194525/https://www.rba.gov.au/payments-and-infrastructure/central-bank-digital-currency/pdf/project-atom-report_2021-12.pdf}

  \item Z. J. Williamson, ``The AZTEC Protocol,'' AZTEC, United Kingdom, Dec. 2018, [Online]. Available: \url{https://github.com/AztecProtocol/AZTEC/blob/develop/AZTEC.pdf}

  \item G. Yu, ``Blockchain Stealth Address Schemes,'' in Cryptology ePrint Archive, Paper 2020/548, 2020.

% SECTION 5

\item Sveriges Riksbank, ``E-krona pilot: Phase 1,'' Sweden, Apr. 2021, [Online]. Available: \url{https://web.archive.org/web/20230325225229/https://www.riksbank.se/globalassets/media/rapporter/e-krona/2021/e-krona-pilot-phase-1.pdf}

  \item Sveriges Riksbank, ``E-krona report: E-krona pilot Phase 2,'' Sweden, Apr. 2022, [Online]. Available: \url{https://web.archive.org/web/20221205234709/https://www.riksbank.se/globalassets/media/rapporter/e-krona/2022/e-krona-pilot-phase-2.pdf}

 \item G. Calle and D. Eidan, ``Central Bank Digital Currency: an innovation in payments,'' r3, Apr. 2020, [Online]. Available: \url{https://web.archive.org/web/20230115033415/https://www.r3.com/wp-content/uploads/2020/04/r3_CBDC_report.pdf}

  \item World Economic Forum, ``Privacy and Confidentiality Options for Central Bank Digital Currency'', Digital Currency Governance Consortium, no. 6/8, 2021. [Online]. Available: \url{https://web.archive.org/web/20221116093951/https://www3.weforum.org/docs/WEF_Privacy_and_Confidentiality_Options_for_CBDCs_2021.pdf}

  \item M. Hearn and R. G. Brown, ``Corda: A distributed ledger,'' Aug. 2019, [Online]. Available: \url{https://web.archive.org/web/20230326172906/https://www.r3.com/wp-content/uploads/2019/08/corda-technical-whitepaper-August-29-2019.pdf}.

\item R3, ``AbstractParty.'' Corda. \url{https://web.archive.org/web/20230423051818/https://docs.r3.com/en/api-ref/corda/4.8/open-source/kotlin/corda/net.corda.core.identity/-abstract-party/index.html}.

\item R3, ``Transaction tear-offs.'' Corda Enterprise 4.7. \url{https://web.archive.org/web/20230423052421/https://docs.r3.com/en/platform/corda/4.7/enterprise/key-concepts-tearoffs.html}.

% SECTION 6
  \item L. Stenbacka, ``The E-krona and Traceability of Your Payment Data: An analysis of the fundamental differences and privacy-related impacts of the Riksbank’s e-krona pilot in comparison with card-based transactions,'' M.S. thesis, Uppsala universitet, Sweden, 2022. [Online]. \url{https://web.archive.org/web/20230420084327/https://www.diva-portal.org/smash/get/diva2:1726955/FULLTEXT02.pdf}

  \item Q. Yao (2017). ``Two Technical Aspects of CBDC in a Two-Tiered System'' [Presentation]. Available: \url{https://web.archive.org/web/20230416043404/https://www.itu.int/en/ITU-T/Workshops-and-Seminars/20180718/Documents/Yao\%20Qian.pdf}
  
  \item Q. Yao, ``A systematic framework to understand central bank digital currency,'' \textit{Science China}, vol. 61, pp. 033101:1-033101:8. Mar. 2018. \url{https://doi.org/10.1007/s11432-017-9294-5}
  
  \item Stanford University, ``Lexicon: `Controllable Anonymity' or ‘Managed Anonymity’ and China’s Digital Yuan.'' DigiChina. \url{https://web.archive.org/web/20230228204724/https://digichina.stanford.edu/work/lexicon-controllable-anonymity-or-managed-anonymity-and-chinas-digital-yuan/}
  
\end{enumerate}
